\documentclass[../Main.tex]{subfiles}

\begin{document}
    \subsection{Overview}
        Overall, I believe that all the objectives have been completed to produce a playable game that has a rouge-like dungeon crawler aspect to it, as you can see in the Testing section of this report. The game has a start, exploration and the end providing to be quite difficult at times, which gives the player a challenge to try and beat the game, with a completely random maze generated each time, it can be quite fun to explore the maze and try to find the exit. The game also allows for the player to gather followers which allows the player to store more items in the followers inventory as well as making it easier in battle. As I have finished development of the game I have enjoyed playing it to see if I can beat the maze and find the exit.
    \subsection{User Feedback}
        I gave my game to an end-user to see what they thought of the game and how easy it was to play.
        \subsubsection{Feedback}
            \begin{itemize}
                \item They enjoyed playing the game and interacting with followers and collecting different items.
                \item The graphics were very good and immersive making it easy to see what you were doing.
                \item The walking in the game was very smooth as some games it can be "sticky".
                \item The different weapons that you can find and use are extremely fun to play around with and use, with the different effects.
                \item The menu system was very simple and easy to use (I did not give any input and he seemed to easily figure what each sections do).
                \item The enemies you have to fight are way too hard to defeat when you are starting off, so they should adapt to your ability as the game progresses.
                \item When you defeat an enemy you should be able to get their weapon, instead of them just disappearing when they die.
                \item The spawn rate of chests are too high, as its too easy to gain all the weapons at the beginning of the game.
            \end{itemize}
        \subsubsection{Reflection}
            I definitely agree with the improvements of making chests harder to find as well as making the enemy AI easier (as mentioned later) and if I had time I would definitely try to improve those. My mistake while programming the current AI was to focus on the range of attacks and not the time and patience of the enemy, which results with the enemy running around super fast all over the place, making it hard for the player to keep track of it. With the balance of the games chests, I definitely think there is room for improvement to find the best balance of the game, however that takes a lot of changing variables slightly and playing through the game multiple times to see how easy or difficult it was, which I did not have time for. Furthermore, the enemies dropping their weapon would be a great implementation, however I did not have the ability to create an object that stored the inventory when a mob died, which lead me to skip this as I believed that it did not bring much to the exploration, instead just being a cool momento and prize to when you have killed an enemy
    \subsection{Improvements}
        As this is a game, there are lots of room for improvement, I have chosen a few catagories that I believe would be the first things I would try to improve in the game.
        \subsubsection{Enemy AI}
            As stated above, the enemy battles are too hard to try and beat, this could have a range of different causes, however I believe the main one to be that they are too fast and hard to keep track of. This was due to me focusing on the range of abilities they had while attacking to make it so that they were not always attacking. However this has made them almost convoluted with random moves that are very confusing.

            So to improve this I believe the enemies would need to be slowed down by having a more advanced delay system in. Also, I have noticed in other games that the enemies do not know the exact position of the player, when they start an attack the player can move, and the enemy will not instantly realise this and change its strategy. This allows the player to exploit weaknesses generated by the enemies.

            Another improvement to this is giving the effect where the enemies will change the difficulty of the fight depending on how advanced the player is at that point in time, so that there is not this one constant (albeit random) attack strategy. This would make the game more of a constant challenge, instead of being extremely hard at the start and then extremely easy.

            Furthermore, the prize is not a lot for killing the enemy, as you do not gain anything, which could result in the players just avoiding the rooms that have enemies in (this could be reduced by the lighting feature talked about earlier). So a simple addition would be add an object that stores the enemies inventory when it dies, which the player can then click on to gain the enemies items.

        \subsubsection{Levels}
            At the moment, there is only one level to the game. This means that it is quiet short and can quickly be beaten. However a good addition would be to have multiple levels that the player could explore, where the enemies get harder and better loot can be found (reducing the risk that the player could quickly become very over powered from their first chest).

            These would add a more immersive experience in the game and allow more exploration to be done, as for each level the generation could be slightly different, or result in different types of rooms (spoken about in the Room Variety section). Furthermore, a boss could be implemented at the end of each level, making a challenge for getting to the next stage of the game and also cause the player to be at a certain point before they can progress.

            However, if this feature was to be implemented, a saving feature would also have to go along with it as, as the levels get longer, the less likely a person is going to finish it in one sitting.

        \subsubsection{Lighting}
            An interesting feature, however much more advanced one, would be to have lighting, where in rooms there would be lights, or no lights, and the player cannot see round corners. This could make the game more enticing by adding an element of surprise, if they stumble into a room with an enemy that was hiding round the corner.

            Also, with this joint with the more levels idea, the game could slowly get darker as the game moves on and you go further into the maze, causing the player to have to find a light source in a chest. This would add to the adventure of the game, as to get past certain sections, you must have found an item to progress, which would force the player to venture further into the maze.

        \subsubsection{Sound}
            At the moment there is no sound in the game, as it I would have had to create a system for playing sounds and when they would be triggered, as well as having to record them. However it would add a lot of immersion into the game to hear when a projectile hits something or when you are firing a projectile.Also, you could get atmospheric music to create a spooky atmosphere when adventuring into the maze.

            A great feature to complement this would be to have followers talk and make jokes as they are following you around the maze. This could be paired with a proper dialog system to allow the player to interact more to the followers and even have more control over what they do, for example their attacking style, or just have conversations to gain knowledge of the followers backstory.

        \subsubsection{Room Variety}
            Another great addition would be different rooms with different styles, for example one could be more run down than another and have a different wall variant other than the stone that is implemented at the moment. This would make adventuring better as you find different room types. However this would need a lot of different sprites to be make for every different style you add.

            Also, there could be more room types, such as different variants of traps, which would make it harder to spot traps and avoid them. Also there could be different exits to the maze which would add a lot more variety into the game. Also the different rooms would allow for different effects to be found or you could even have different weapons found in the different types of rooms.

        \subsubsection{Stats}
            At the moment, the stats the player starts with are the stats that they keep throughout the game, not being able to change them. However, having a system that allowed the player to improve there stats after moving a certain number of tiles or killing a certain number of enemies would add purpose for exploration and attacking enemies.

            Furthermore, stats should play more of a role in different aspects of the game, which would allow the player to take different strategies to playing, either choosing speed to explore more over attack strength, or in the case of lighting, choose to be able to see further and behind walls over attacking ability.

        \subsubsection{Tutorial}
            The game does not have any explanation or tutorial at the moment, so it is quiet hard for a new person to easily get the hang of how it woulds (even though when I gave it to an end user they seemed to be able to navigate and understand the game pretty quickly). It would be very useful to have an easy way to explain the aim of the game. For example, before you go into the maze having a couple of rooms generate and have text on the screen to show you what to do.

        \subsubsection{Better Structure}
            This would be a minor improvement, however, I believe it's worth mentioning. The current structure to the code is slightly mangled and has in the past caused circular imports (talked about in the Testing section). So a revamp of how the program is structured would definitely improve the ability to add new things to it. For example, there should be more layers that handle different tasks of the program. So for example having a layer for just holding and handling all the entities, and one for handling just the tiles and rooms. This would reduce the amount of circular imports and allow more flexibility when programming.
\end{document}